Properties of winning Iterated Prisoner's Dilemma strategies.

### 2020-03-29 paper/main.tex
finalise evaluation section

Though there is not a single strategy that repeatably outranks all others in any
of the distinct tournament types, or even across the tournaments type, there
are specific types of strategies have been repeatably ranked in the top ranks.
These have been strategies that have been trained, strategies that defected
and strategies that would adapt their behaviour based on preassigned rules
to achieve the highest outcome. These results contradict Axelrod's suggestions,
and more specifically, the suggestions `Do not be clever' and `Do not be envious'.

@@

The aim of this section is to explore the features that contribute to a
strategy's successful performance. The features explored are measures regarding a
strategy's behaviour, along with measures regarding the tournaments the
strategies competed in. A summary of the features is given in
Table~\ref{table:manual_features}.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{gcgcgc}
    \toprule
    feature & feature explanation &  source & value type & min value & max value \\
    \midrule
stochastic  &  If a strategy is stochastic & strategy classifier from APL & boolean  & Na &  Na \\
makes use of game &  If a strategy makes used of the game information & strategy classifier from APL & boolean  & Na &  Na \\
makes use of length &  If a strategy makes used of the number of turns & strategy classifier from APL & boolean  & Na &  Na \\
memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in a given tournament  & result summary  & float & 0 & 1 \\
$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
$C_{\text{min}}$ / $C_r$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & result summary  & float & 0 & 1 \\
$C_r$ & The cooperating ratio of a strategy & result summary  & float & 0 & 1 \\
$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary  & float & 0 & 1\\
$CD$ to $C$ rate & The probability a strategy will cooperate after being betrayed by the opponent & result summary  & float & 0 & 1 \\
$DC$ to $C$ rate & The probability a strategy will cooperate after betraying the opponent & result summary  & float & 0 & 1 \\
$DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary  & float & 0 & 1 \\
$p_n$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
$n$ & The number of turns & trial summary & integer & 1 & 200 \\
$p_e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
$N$ & The number of strategies in the tournament & trial summary & integer & 3 & 195 \\
$k$ & The number of repetitions of a given tournament & trial summary & integer & 10 & 100 \\
    \bottomrule
        \end{tabular}}
    \end{center}
    \caption{The features which are included in the performance evaluation analysis.}
    \label{table:manual_features}
\end{table}

APL classifies strategies along several dimensions. These determine whether
a strategy is stochastic or deterministic, whether it makes use of the number of
turns or the game's payoffs. The memory usage feature is calculated as the
memory size of strategy (which is specified in the strategies implementation
in the APL) divide by the number of turns. For example, Winner12 has a memory
size of 2 and participated in a tournament where $n$ was 101. In the given
tournament Winner12 has a memory usage of 0.014925. There are strategies with
an infinite memory size, for example Evolved FSM 16 Noise 05. These strategies
have a memory usage of 1.
For tournaments with a probabilistic ending the number of turns was
not collected, so the memory usage feature is not used for probabilistic ending
tournaments. The SSE is a feature introduced in~\cite{Knight2019} which shows
how close a strategy is to behaving as a ZDs, and subsequently, in an
extortionate way. The method identifies the ZDs closest to a given strategy and
calculates the algebraic distance between them, defined as SSE. A SSE value of 1
indicates no extortionate behaviour at all whereas a value of 0 indicates that a
strategy is behaving a ZDs. The rest of the features considered are the $CC$ to
$C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as cooperating
ratio of a strategy. The minimum, maximum, medium and median cooperating ratios
of each tournament are also included, and finally the number of turns, the
number of strategies, the number of repetitions and the probabilities of noise
and the game ending are also included.

Table~\ref{table:correlations} shows the correlation coefficients between the
features of Table~\ref{table:manual_features} the median score and the median
normalised rank. Note that the correlation for the classifiers is
not included because they are binary variables and they will be evaluated using a
different method. The correlation coefficients for all the features in
Table~\ref{table:manual_features} against themselves have also been calculated and a
graphical representation can be found in the Appendix~\ref{app:correlations}.

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
    \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
    standard tournaments.}\label{fig:rates_of_winners_in_standard_tournaments}
\end{figure}

Compared to standard tournaments, in both noisy and in probabilistic ending
tournaments the higher the rates of cooperation the lower a strategy's success
and median score. A strategy would want to cooperate less than both
the mean and median cooperator in such settings. In probabilistic ending
tournaments the correlation coefficients have a larger values, indicating a
stronger effect. Thus a strategy will be punished more by its cooperative
behaviour in probabilistic ending environments, this was seen in Section~\ref{section:evaluation_of_performance}
as well. The distributions of the $C_r$ of the winners in
both tournaments is given by Figure~\ref{fig:c_r_distributions}. It confirms
that the winners in noisy tournaments cooperated less than 35\% of the times
and in probabilistic ending tournaments less than 10\%.
In noisy probabilistic ending tournaments and in over all the tournaments' results,
the only features that had a moderate affect are $C_r/C_{\text{mean}},
C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
appears to be punished by not as much as in noisy and probabilistic ending
tournaments.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.65\textwidth]{../images/c_r_winners_tournaments.pdf}
    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
    ending tournaments.}\label{fig:c_r_distributions}
\end{figure}

A multivariate linear regression is fitted to model the relationship of
Table's~\ref{table:manual_features} and the normalised rank. Based on the
correlation matrices. Appendix~\ref{app:correlations} the depended variables are
correlated. The median cooperating ration \(C_median\) and \(C_r/ C_median\) are highly
correlated with \(C_mean\) and \(C_r / C_mean\). So these features are dropped from
the analysis. The \(C_r\) is also correlated and drop. Finally for some environments
the \(C_max\) and \(C_min\) are correlated and dropped for the models of those types.
More specifically, the list of features their p values and \(p-\)values of
each feature as well as their coefficients are given by
Table~\ref{table:linear_regression}. The coefficient of determination, \(R\)
squared, for each model is also reported in Table~\ref{table:linear_regression}.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
\resizebox{.8\textwidth}{!}{
    \input{regression_table.tex}}
    \end{center}
    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.}
    \label{table:linear_regression}
\end{table}

The results of the linear regression verify the results of the previous
approaches. The only features that do no have a significant effect on the
models are the number of repetitions and memory usage in noisy tournaments,
and the number of turns, number of repetitions and thr probability \(p_e\) in
probabilistic ending tournaments. Over all the models, the features that are the
most important predictors are $C_r$, $C_r$ / $C_{max}$ and $C_r$ / $C_{mean}$.

The features $C_{r} / C_{median}$ and $C_r / C_{mean}$ have been repeatably
highlighted as importance features in explaining the variability of the performances.
Thus, the effect of these two measures is further explored. In
Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
and \(C_r / C_{\text{median}}\) are given for the winners in standard tournaments. A value of \(C_r /
C_{\text{mean}} = 1\) imply that the cooperating ratio of the winner was the
same as the mean/median cooperating ratio of the tournament. In standard tournaments, the mean
for both ratios is 1. Therefore, an effective strategy in standard tournaments
was the mean/median cooperator of its respective tournament. In comparison,
Figure~\ref{fig:mean_median_noisy} shows the distributions of the features for
the winners in noisy tournaments where the mean is at 0.67. Thereupon the winners
cooperated 67\% of the times the mean/median cooperator did. This analysis is
applied to the rest of the tournaments and the distributions are given by
Figures \ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
\ref{fig:mean_median_overall}. In a tournament with noisy and a probabilistic
ending the winners cooperated 60\%, whereas in settings that the type of the
tournament can vary between the types considered in this work the winners
cooperated 67\% of the times the mean or median cooperator did. Finally, in
probabilistic ending tournament it has already been mentioned that defecting
strategies prevail and this result is once again confirmed in this section.

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/compared_to_mean_standard.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of standard tournaments.}
        % \label{fig:noisy_probend_results}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/sse_standard.pdf}
        \caption{Distributions of SSE for winners of standard tournaments.}
        % \label{fig:overall_results}
    \end{subfigure}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/compared_to_mean_noisy.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy tournaments.}
        % \label{fig:noisy_probend_results}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/sse_noisy.pdf}
        \caption{Distributions of SSE for winners of noisy tournaments.}
        % \label{fig:overall_results}
    \end{subfigure}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of probabilistic ending tournaments.}
        % \label{fig:noisy_probend_results}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/sse_probend.pdf}
        \caption{Distributions of SSE for winners of probabilistic ending tournaments.}
        % \label{fig:overall_results}
    \end{subfigure}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.5\textwidth]{../images/cd_to_c_probend.pdf}
    % \caption{Distributions of \(C_r / C_{\text{median}}\)
    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend_noisy.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
        % \label{fig:noisy_probend_results}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/sse_probend_noisy.pdf}
        \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
        % \label{fig:overall_results}
    \end{subfigure}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_probend_noisy_tournaments.pdf}
    % \caption{Distributions of \(C_r / C_{\text{median}}\)
    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/compared_to_mean_overall.pdf}
        % \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
        % \label{fig:noisy_probend_results}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/rate_overall.pdf}
        % \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
        % \label{fig:overall_results}
    \end{subfigure}
\end{figure}

In this section the effect of several features, regarding a strategy's behaviour
and the tournament in which it participated on its performance were presented.
This was done using three methods. Correlation coefficients, a random forest
analysis and a linear regression. The results of these are summarised in the following section.

>>>>

Though there is not a single strategy that repeatably outranks all others in any
of the distinct tournament types, or even across the tournaments type, there
are specific types of strategies have been repeatably ranked in the top ranks.
These have been strategies that have been trained, strategies that defected
and strategies that would adapt their behaviour based on preassigned rules
to achieve the highest outcome. These results contradict Axelrod's suggestions,
and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
The features and properties contributing a strategy's success are further
explored in Section~\ref{section:evaluation_of_performance}.

@@

The performance of the strategies is evaluated based on the features of
Table~\ref{table:manual_features}. These feature are measures regarding a
strategy's behaviour and the tournaments the strategies competed in are
explored.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{.99\textwidth}{!}{
    \begin{tabular}{gcgcgc}
    \toprule
    feature & feature explanation &  source & value type & min value & max value \\
    \midrule
stochastic  &  If a strategy is stochastic & strategy classifier from APL & boolean  & Na &  Na \\
makes use of game &  If a strategy makes used of the game information & strategy classifier from APL & boolean  & Na &  Na \\
makes use of length &  If a strategy makes used of the number of turns & strategy classifier from APL & boolean  & Na &  Na \\
memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in a given tournament  & result summary  & float & 0 & 1 \\
$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
$C_{\text{min}}$ / $C_r$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & result summary  & float & 0 & 1 \\
$C_r$ & The cooperating ratio of a strategy & result summary  & float & 0 & 1 \\
$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary  & float & 0 & 1\\
$CD$ to $C$ rate & The probability a strategy will cooperate after being betrayed by the opponent & result summary  & float & 0 & 1 \\
$DC$ to $C$ rate & The probability a strategy will cooperate after betraying the opponent & result summary  & float & 0 & 1 \\
$DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary  & float & 0 & 1 \\
$p_n$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
$n$ & The number of turns & trial summary & integer & 1 & 200 \\
$p_e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
$N$ & The number of strategies in the tournament & trial summary & integer & 3 & 195 \\
$k$ & The number of repetitions of a given tournament & trial summary & integer & 10 & 100 \\
    \bottomrule
        \end{tabular}}
    \end{center}
    \caption{The features which are included in the performance evaluation
    analysis. stochastic, makes use of game and makes use of game are APL
    classifies that determine whether a strategy is stochastic or deterministic,
    whether it makes use of the number of turns or the game's payoffs. The
    memory usage is calculated as the number of turns the strategy considers to
    make an action (which is specified in the APL) divide by the number of
    turns. The SSE (introduced in~\cite{Knight2019}) shows how close a strategy
    is to behaving as a ZDs, and subsequently, in an extortionate way. The
    method identifies the ZDs closest to a given strategy and calculates the
    algebraic distance between them, defined as SSE. A SSE value of 1 indicates
    no extortionate behaviour at all whereas a value of 0 indicates that a
    strategy is behaving a ZDs. The rest of the features considered are the $CC$
    to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
    cooperating ratio of a strategy, the minimum (\(C_{min}\)), maximum
    (\(C_{max}\)), mean (\(C_{mean}\)) and median (\(C_{median}\)) cooperating
    ratios of each tournament.}
    \label{table:manual_features}
\end{table}

The memory usage of strategies with an infinite memory size, for example Evolved
FSM 16 Noise 05 is 1. There rest is calculated as explained in Table
\ref{table:manual_features}. For example,  Winner12 has a memory size of 2 and
participated in a tournament where $n$ was 101. In the given tournament Winner12
has a memory usage of 0.014925. Note that for tournaments with a probabilistic
ending the number of turns was not collected, so the memory usage feature is not
used for probabilistic ending tournaments.

The correlation coefficients between the features of
Table~\ref{table:manual_features} the median score and the median normalised
rank are given by Table~\ref{table:correlations}. The correlation coefficients
between all features of Table~\ref{table:manual_features} have been calculated
and a graphical representation can be found in the
Appendix~\ref{app:correlations}.

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.57\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
    \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
    standard tournaments.}\label{fig:rates_of_winners_in_standard_tournaments}
\end{figure}

Compared to standard tournaments, in both noisy and in probabilistic ending
tournaments the higher the rates of cooperation the lower a strategy's success
and median score. A strategy would want to cooperate less than both
the mean and median cooperator in such settings. In probabilistic ending
tournaments the correlation coefficients have a larger values, indicating a
stronger effect. Thus a strategy will be punished more by its cooperative
behaviour in probabilistic ending environments, supporting the results of Section~\ref{section:evaluation_of_performance}
as well. The distributions of the $C_r$ of the winners in
both tournaments are given by Figure~\ref{fig:c_r_distributions}. It confirms
that the winners in noisy tournaments cooperated less than 35\% of the times
and in probabilistic ending tournaments less than 10\%.
In noisy probabilistic ending tournaments and in over all the tournaments' results,
the only features that had a moderate affect are $C_r/C_{\text{mean}},
C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
appears to be punished by not as much as in noisy and probabilistic ending
tournaments.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.57\textwidth]{../images/c_r_winners_tournaments.pdf}
    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
    ending tournaments.}\label{fig:c_r_distributions}
\end{figure}

A multivariate linear regression has been fitted to model the relationship between
the features and the normalised rank. Based on the graphical representation of
the correlation matrices given in Appendix~\ref{app:correlations} several of the
features are highly correlated. Highly correlated features have been removed
before fitting the linear regression model. The features included are given
by Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
in the distinct tournaments and their regression coefficients.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
\resizebox{.8\textwidth}{!}{
    \input{regression_table.tex}}
    \end{center}
    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.
    \(R\) square is reported for each model. An \(R\) square of 1 represents a model
    that explains all of the variation in the response variable around its mean.}
    \label{table:linear_regression}
\end{table}

The feature \(C_{r} / C_{\text{mean}}\) has a statistically significant effect
across all models and a high regression coefficient. It has both a positive and
negative impact on the normalised rank depending on the environment. For
standard tournaments, Figure~\ref{fig:discussion_standard} gives the
distributions of several features for the winners of standard tournaments. The
\(C_{r} / C_{\text{mean}}\) distribution of the winner is also given in
Figure~\ref{fig:discussion_standard}. A value of \(C_r / C_{\text{mean}} = 1\)
implies that the cooperating ratio of the winner was the same as the mean
cooperating ratio of the tournament, and in standard tournaments, the median is
1. Therefore, an effective strategy in standard tournaments was the mean
cooperator of its respective tournament.

The distributions of SSE and \(CC\) to \(D\) rate for the winners of standard
tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
distributions for the winners indicate that they strategy's behaved in ZD way in
several tournaments, however, not constantly. The winners participated in
matches where they did not try to extortionate their opponents. Futhermore, the
\(CC\) to \(D\) distribution indicates that if a strategy were to defect against
the winners they would reciprocate on average with a probability of 0.5.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/standard_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of standard tournaments. A
        value of \(C_r / C_{\text{mean}} = 1\) imply that the cooperating ratio of the
        winner was the same as the mean cooperating ratio of the tournament. An SSE distribution
        skewed towards 0 indicates a ZD behaviour by the strategy.}
        \label{fig:discussion_standard}
\end{figure}

Similarly for the reset of the different tournaments types, and the entire data
set the distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
are given by Figures~\ref{fig:discussion_noisy},~\ref{fig:discussion_probend},
\ref{fig:discussion_probend_noisy} and~\ref{fig:discussion_entire_data}.

Based on the \(C_r / C_{\text{mean}}\) distributions the successful strategies
have adapted differently to the mean cooperator depending on the tournament
type. In noisy tournaments where the median of the distribution is at 0.67, and
thereupon the winners cooperated 67\% of the times the mean cooperator did. In
tournaments with noise and a probabilistic ending the winners cooperated 60\%,
whereas in settings that the type of the tournament can vary between all the
types the winners cooperated 67\% of the times the mean cooperator did. Lastly,
in probabilistic ending tournaments it has already been mentioned that defecting
strategies prevail (Section~\ref{section:top_performances}), and this result is
once again confirmed here.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/noisy_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of noisy tournaments.}
        \label{fig:discussion_noisy}
\end{figure}

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit ZD behaviour, but not constantly. ZDs are a set of strategies
that are envious as they try to exploit their opponents. The winners of the
tournaments considered in this work are envious, but not as much as ZDs.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/probend_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of probabilistic ending tournaments.}
        \label{fig:discussion_probend}
\end{figure}

The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
successful strategy after it's opponent has defected against it. In standard
tournaments it was observed that a successful strategy reciprocates with a
probability of 0.5. This is distinct between the tournament types. In
tournaments with noise a strategy is less likely to cooperate following a
defection compared to standard tournaments, and in probabilistic ending
tournaments a strategy will reciprocate a defection. In a setting that the type
of the tournament can vary between all the examined types a winning strategy
would reciprocate on average with a probability of 0.58.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/probend_noisy_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of noisy probabilistic ending tournaments.}
        \label{fig:discussion_probend_noisy}
\end{figure}

Further statistically significant features with strong effects include \(C_r /
C_{\text{min}}\), \(C_r / C_{\text{max}}\), \(C_{\text{min}}\) and
\(C_{\text{max}}\). These add more emphasis on how important it is for a  a
strategy to adapt to it's environment. Finally, the features number of turns,
repetitions and the probabilities of noise and the game ending had not
significant effect based on the multivariate regression models.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/entire_data_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners over the tournaments of the entire data set.}
        \label{fig:discussion_entire_data}
\end{figure}

A third method that evaluates the importance of the features in
Table~\ref{table:manual_features} has been carried out and it can be found in
the Appendix~\ref{app:clustering}. The results uphold the outcomes of the
correlation and multivariate regression methods. It also evaluates the effects
of the classifiers stochastic, make use of game and make use of length which
have not been evaluated by the methods above because there are binary variables.
The results imply that they have no significant effect on a strategy's
performance.
